Budgeted Reinforcement Learning in Continuous State Space

### 2019-11-24 paper/talk/nicolas/talk-autonomous-driving-oriented.tex
Rewrite talk with the new inria template

\title[]{Budgeted Reinforcement Learning in Continuous State Space}
\date{10 august 2018.}
\begin{document}
    \begin{frame}
        \maketitle
        \centering
    \end{frame}

    \foreach \n in {0,1,2,3,4,5}{
    \begin{frame}{\textbf{Introduction} | Use-case}
        \begin{figure}
            \centering
            \includegraphics[scale=0.5]{talk/img/\n}
        \end{figure}
    \end{frame}
    }

    \begin{frame}{\textbf{Introduction} | Use-case}
        \begin{block}{Problem}
            Given past trajectories, find a way to:
            \begin{itemize}
                \pause\item gather gold as much as possible;
                \pause\item limit the villager casualties under some budget;
                \pause\item being able to change the budget in real time.
            \end{itemize}

@@

    \foreach \n in {0,1,2,3,4}{
    \begin{frame}{The Dynamic Programming solution: intuition}
        \begin{figure}
            \centering
            %%\vspace{-1.5em}
            \includegraphics[scale=0.6,page=1]{talk/img/a\n}
        \end{figure}
    \end{frame}
    }

@@

        \textbf{Domain}
        \begin{itemize}
                \pause\item States $\ocS = \cS\times\cB$.
                \pause\item Actions $\ocA = \cA\times\cB$.
                \pause\item Dynamics $\ov{P}\left((s',\beta') \condbar (s,\beta), (a, \beta_a)\right) \eqdef P(s'|s, a)\delta(\beta' - \beta_a)$.
                \end{itemize}
        \textbf{2D  signals}
        \begin{enumerate}
            \pause\item Rewards $R = (R_r, R_c)$
            \pause\item Returns $G^\pi = (G_r^\pi, G_c^\pi)$
            \pause\item $V^\pi(\os) = (V_r^\pi, V_c^\pi) \eqdef \expectedvalue\left[ G^\pi \condbar \ov{s_0} = \os\right]$
                \pause\item $Q^\pi(\os, \oa)= (Q_r^\pi, Q_c^\pi) \eqdef \expectedvalue\left[ G^\pi \condbar \ov{s_0} = \os, \ov{a_0} = \oa\right]$
        \end{enumerate}

@@

    \begin{frame}{Augmented Optimality}
        \begin{definition}In that order, we want to:
\begin{enumerate}
    \item[(i)] \pause\colorbox{red}{Respect the budget $\beta$}: 
    \begin{equation*}
    \Pi_a(\os) \eqdef \{\pi\in\Pi: V_c^\pi(s, \beta) \mathcolorbox{red}{\leq \beta}\}
    \end{equation*}
    \item[(ii)] \pause\colorbox{green}{Maximise the rewards}:
    \begin{equation*}
        V_r^*(\os) \eqdef \mathcolorbox{green}{\max}_{\pi\in\Pi_a(\os)}  V_r^\pi(\os) \qquad\quad \Pi_r(\os) \eqdef \mathcolorbox{green}{\argmax}_{\pi\in\Pi_a(\os)}  V_r^\pi(\os)
    \end{equation*}
    \item[(iii)] \pause\colorbox{yellow}{Minimise the costs}: 
    \begin{equation*}
        V_c^*(\os) \eqdef \mathcolorbox{yellow}{\min}_{\pi\in\Pi_r(\os)}  V_c^\pi(\os), \qquad\quad \Pi^*(\os) \eqdef \mathcolorbox{yellow}{\argmin}_{\pi\in\Pi_r(\os)}  V_c^\pi(\os)
    \end{equation*}
\end{enumerate}

@@

    \foreach \n in {0,1,2}{
    \begin{frame}{Not a contraction: intuition}
        \begin{figure}
            \centering
            %%\vspace{-1.5em}
            \includegraphics[scale=0.9,page=1]{talk/img/d\n}
        \end{figure}
    \end{frame}
    }

    \begin{frame}{Contractivity on smooth $Q$-functions}
        \begin{conjecture}[Contractivity $\cL_\gamma$]
            $\cT$ is a contraction when restricted to the subset $\cL_\gamma$ of $Q$-functions such that "$Q_r$ is $L$-Lipschitz with respect to $Q_c$", with $L<\frac{1}{\gamma}-1$.
        \end{conjecture}

@@

    \end{frame}
    \begin{frame}{Experiments: dialogue systems}
        \begin{center}
            \includegraphics[width=\textwidth]{talk/img/slot-filling.pdf}
        \end{center}
    \end{frame}

    \begin{frame}{Experiments: autonomous driving}
        \begin{itemize}
            \item the agent (the car) is on a two-way road with a car in front of it, two solutions: 
            \begin{itemize}
                \item it can stay behind (safe/slow);
                \item it can overtake (unsafe/fast).
            \end{itemize}
        \end{itemize}
    \end{frame}
    \begin{frame}{Experiments: autonomous driving}
        \begin{center}
            \includegraphics[width=\textwidth]{talk/img/highway.pdf}
        \end{center}
    \end{frame}

    \begin{frame}{Experiments: autonomous driving}
        \href{scaling-up-brl.github.io-master/highway-env.html}{\beamergotobutton{BFTQ on the highway environment}}

@@

        \begin{columns}
            \begin{column}{0.7\textwidth}
                \begin{itemize}
                    \item 2 corridors:
                    \begin{itemize}
                        \item high costs/high rewards around the starting state
                        \item no costs/low rewards around the starting state
                    \end{itemize}
                    \item The outermost cells are the ones yielding the most reward
                \end{itemize}
            \end{column}
            \begin{column}{0.3\textwidth}  %%<--- here
                \begin{center}
                    \includegraphics[width=\textwidth]{talk/img/env-corridor.pdf}
                \end{center}
            \end{column}
        \end{columns}

@@

        \begin{columns}
            \begin{column}{0.7\textwidth}
                \includegraphics[page=1, width=\textwidth]{talk/img/corridors}
            \end{column}
            \begin{column}{0.3\textwidth}  %%<--- here
                \begin{center}
                    \includegraphics[width=\textwidth]{talk/img/test.pdf}
                \end{center}
            \end{column}
        \end{columns}
    \end{frame}

    \begin{frame}{Experiments: corridors}
        \href{scaling-up-brl.github.io-master/corridors.html}{\beamergotobutton{Risk-sensitive vs Risk-Neutral on the corridors environment}}

>>>>

\title[]{Budgeted Reinforcement Learning in Continuous State Space}
\date{November the 14th, 2019.}
\begin{document}
    \begin{frame}
        \maketitle
        \centering
    \end{frame}

    \begin{frame}{\textbf{Introduction} | Context}
        \begin{itemize}
            \item The \textbf{autonomous driving} problem is hard to solve. Why ?
            \begin{itemize}
                \item we need to model the physic laws
                \item but also and the human behaviors (negociation/randomness).
            \end{itemize}
            \item \textbf{Reinforcement Learning} is a solution, but
            \begin{itemize}
                \item It only works with one reward signal.
                \item Reward is hard to design, need a lot of tuning
                \item It usually implies too conversatives or too risky behaviors.
            \end{itemize}

            \item \textbf{Robust Control} faces the same problem.
            \begin{itemize}
                \item Propagating the incertitudes implies too safe behaviors.
                \item Models used have to be simple and it can't apply in sim2real.
            \end{itemize}
            \item The solution: \textbf{Safe Reinforcement Learning}
            \begin{itemize}
                \item Control the risk and the reward signal.
                \item Keeps the objectives simple.
                \item Add a new DOF: easier to design a more complexe reward.
            \end{itemize}
        \end{itemize}
    \end{frame}

    \begin{frame}{\textbf{Introduction} | Problem}
        \begin{block}{Problem}
            Given past trajectories, find a way to:
            \begin{itemize}
                \pause\item maximize a signal;
                \pause\item limit the frequency of catastrophic events given some budget;
                \pause\item being able to change the budget in real time.
            \end{itemize}

@@

    \foreach \n in {0,1,2,3,4}{
    \begin{frame}{The Dynamic Programming solution: intuition}
        \begin{figure}
            \centering
            %%\vspace{-1.5em}
            \includegraphics[scale=0.6,page=1]{img/a\n}
        \end{figure}
    \end{frame}
    }

@@

        \textbf{Domain}
        \begin{itemize}
            \pause\item States $\ocS = \cS\times\cB$.
            \pause\item Actions $\ocA = \cA\times\cB$.
            \pause\item Dynamics $\ov{P}$ %$\ov{P}\left((s',\beta') \condbar (s,\beta), (a, \beta_a)\right) \eqdef P(s'|s, a)\delta(\beta' - \beta_a)$.
        \end{itemize}
        \textbf{2D signals}
        \begin{enumerate}
            \pause\item Rewards $R = (R_r, R_c)$
            \pause\item Returns $G^\pi = (G_r^\pi, G_c^\pi)$
            \pause\item $V^\pi(\os) = (V_r^\pi, V_c^\pi) \eqdef \expectedvalue\left[ G^\pi \condbar \ov{s_0} = \os\right]$
            \pause\item $Q^\pi(\os, \oa)= (Q_r^\pi, Q_c^\pi) \eqdef \expectedvalue\left[ G^\pi \condbar \ov{s_0} = \os, \ov{a_0} = \oa\right]$
        \end{enumerate}

@@

    \begin{frame}{Augmented Optimality}
        \begin{definition}
            In that order, we want to:
            \begin{enumerate}
                \item[(i)] \pause\colorbox{red}{Respect the budget $\beta$}:
                \begin{equation*}
                    \Pi_a(\os) \eqdef \{\pi\in\Pi: V_c^\pi(s, \beta) \mathcolorbox{red}{\leq \beta}\}
                \end{equation*}
                \item[(ii)] \pause\colorbox{green}{Maximise the rewards}:
                \begin{equation*}
                    V_r^*(\os) \eqdef \mathcolorbox{green}{\max}_{\pi\in\Pi_a(\os)}  V_r^\pi(\os) \qquad\quad \Pi_r(\os) \eqdef \mathcolorbox{green}{\argmax}_{\pi\in\Pi_a(\os)}  V_r^\pi(\os)
                \end{equation*}
                \item[(iii)] \pause\colorbox{yellow}{Minimise the costs}:
                \begin{equation*}
                    V_c^*(\os) \eqdef \mathcolorbox{yellow}{\min}_{\pi\in\Pi_r(\os)}  V_c^\pi(\os), \qquad\quad \Pi^*(\os) \eqdef \mathcolorbox{yellow}{\argmin}_{\pi\in\Pi_r(\os)}  V_c^\pi(\os)
                \end{equation*}
            \end{enumerate}

@@

    \foreach \n in {0,1,2}{
    \begin{frame}{Not a contraction: intuition}
        \begin{figure}
            \centering
            %%\vspace{-1.5em}
            \includegraphics[scale=0.9,page=1]{img/d\n}
        \end{figure}
    \end{frame}
    }

    \begin{frame}{Contractivity on smooth $Q$-functions}
        \begin{Theorem}[Contractivity $\cL_\gamma$]
            $\cT$ is a contraction when restricted to the subset $\cL_\gamma$ of $Q$-functions such that "$Q_r$ is $L$-Lipschitz with respect to $Q_c$", with $L<\frac{1}{\gamma}-1$.
        \end{Theorem}

@@

    \end{frame}
    \begin{frame}{Experiments: dialogue systems}
        \begin{center}
            \includegraphics[width=\textwidth]{img/slot-filling.pdf}
        \end{center}
    \end{frame}

    \begin{frame}{Experiments: autonomous driving}
        \begin{itemize}
            \item the agent (the car) is on a two-way road with a car in front of it, two solutions:
            \begin{itemize}
                \item it can stay behind (safe/slow);
                \item it can overtake (unsafe/fast).
            \end{itemize}
        \end{itemize}
    \end{frame}
    \begin{frame}{Experiments: autonomous driving}
        \begin{center}
            \includegraphics[width=\textwidth]{img/highway.pdf}
        \end{center}
    \end{frame}

    \begin{frame}{Experiments: autonomous driving}
        \href{../../assets/highway-env.html}{\beamergotobutton{BFTQ on the highway environment}}

@@

        \begin{columns}
            \begin{column}{0.7\textwidth}
                \begin{itemize}
                    \item 2 corridors:
                    \begin{itemize}
                        \item high costs/high rewards around the starting state
                        \item no costs/low rewards around the starting state
                    \end{itemize}
                    \item The outermost cells are the ones yielding the most reward
                \end{itemize}
            \end{column}
            \begin{column}{0.3\textwidth}  %%<--- here
                \begin{center}
                    \includegraphics[width=\textwidth]{img/env-corridor.pdf}
                \end{center}
            \end{column}
        \end{columns}

@@

        \begin{columns}
            \begin{column}{0.7\textwidth}
                \includegraphics[page=1, width=\textwidth]{img/corridors}
            \end{column}
            \begin{column}{0.3\textwidth}  %%<--- here
                \begin{center}
                    \includegraphics[width=\textwidth]{img/test.pdf}
                \end{center}
            \end{column}
        \end{columns}
    \end{frame}

    %    \begin{frame}{Experiments: corridors}
    %        \href{scaling-up-brl.github.io-master/corridors.html}{\beamergotobutton{Risk-sensitive vs Risk-Neutral on the corridors environment}}
    %
    %    \end{frame}
